---
title: ""  
author: "`r rworkflows::use_badges(add_doi = '10.1093/bioinformatics/btab658')`"
output:
  github_document
---

```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("DESCRIPTION", fields = "Package")[1]
description <- read.dcf("DESCRIPTION", fields = "Description")[1]
```
 
## ``r pkg``: `r gsub("echoverse module: ","", description)`

This R package is part of the *echoverse* suite that supports [`echolocatoR`](https://github.com/RajLabMSSM/echolocatoR):
an automated genomic fine-mapping pipeline. 

If you use ``r pkg``, please cite: 

> `r citation(pkg)$textVersion`

## Installation 

```R
if(!require("remotes")) install.packages("remotes")

remotes::install_github("RajLabMSSM/`r pkg`")
library(`r pkg`)
```
## Documentation 

### [Website](https://rajlabmssm.github.io/`r pkg`) 
### [Get started](https://rajlabmssm.github.io/`r pkg`/articles/`r pkg`) 

## Name 

<details>
<summary><strong>&#129415; So what does <code>devoptera</code> mean, anyways?</strong> (click to find out)</summary>

[__DevOps__](https://en.wikipedia.org/wiki/DevOps) is a software engineering
methodology that is itself an amalgam of software **Dev**lopment and 
IT **Op**eration**s**.

**Chiroptera** is a the name of the phylogenetic order to which bats belong.
`devoptera` is part of the broader *echoverse* suite that supports 
[`echolocatoR`](https://github.com/RajLabMSSM/echolocatoR), and 
`echolocatoR` is an R package that facilitates fine-mapping to pinpoint 
causal genetic variants underlying complex traits.
You know, like bats do (kind of). :cricket::wavy_dash::bat:
</details>

<hr>

## Contact

<a href="https://bschilder.github.io/BMSchilder/" target="_blank">Brian
M. Schilder, Bioinformatician II</a>  
<a href="https://rajlab.org" target="_blank">Raj Lab</a>  
<a href="https://icahn.mssm.edu/about/departments/neuroscience" target="_blank">Department
of Neuroscience, Icahn School of Medicine at Mount Sinai</a>  
 
# Session info

<details> 
```{r Session Info}
devoptera::session_info()
```
</details>   
<hr> 
