---
title: echoverse hex stickers
author: '<h4>Authors: <i>`r auths <- eval(parse(text = gsub("person","c",read.dcf("../DESCRIPTION",
  fields = "Authors@R"))));paste(auths[names(auths)=="given"],auths[names(auths)=="family"],
  collapse = ", ")`</i></h4>'
date: '<h4>Vignette updated: <i>`r format( Sys.Date(), "%b-%d-%Y")`</i></h4>'
output: BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{devoptera}
   %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```


```R
library(`r pkg`)
```

# Make hex

`devoptera::make_hex` is a helper function that generates an `echoverse`-themed hex sticker using a built-in template.

```{r}
hex <- devoptera::make_hex(pkg = "devoptera", 
                           save_path = tempfile(fileext = "hex.png"))
```

# Show hex

By default, it saves the sticker at *inst/hex/hex.png*. Once it's been created, you can push it to the package's GitHub repository.

This will then be detected automatically by `rworkflows::use_badges()` when the argument `use_hex=TRUE`.

```{r, results='asis'}
rworkflows::use_badges(ref = "RajLabMSSM/devoptera",
                       add_hex = TRUE)
```


## Further customisation

For more customised hex stickers, you can make awesome hex stickers for your R packages using:

- [hexSticker](https://github.com/GuangchuangYu/hexSticker)  
- [ggimage](https://github.com/GuangchuangYu/ggimage) 
lets you render images as data points.  
- [ggpattern](https://coolbutuseless.github.io/package/ggpattern/)
lets you fill objects with patterns or images.
- [magick](https://cran.r-project.org/web/packages/magick/vignettes/intro.html) 
modify PNGs.

# Session Info 

<details> 
```{r Session Info}
devoptera::session_info()
```
</details>   
<hr>